Locating Data Flow Anomaly With Statistical Distance

### 2017-08-25 Paper/DataAnomaly/paper.tex
Modify introduction of paper

		\begin{figure}[!t]
			\centering
			\includegraphics[width=0.75\linewidth]{fig/Example}
			\caption{Example Cumulative Distribution Function of Original And Modified Data}
			\label{fig:example}
		\end{figure}

		According to our observation, typical data manipulations on numerical data will lead to the drift of its distribution. For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original. The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions. These anomalies inside data pipelines will severely affect mining and learning algorithms and further change the final decision given by the entire system.

>>>>

		\begin{figure}[!t]
			\centering
			\includegraphics[width=\linewidth]{fig/ExampleEcdf.png}
			\caption{Example Cumulative Distribution Function of Original And Modified Data}
			\label{fig:example-ecdf}
		\end{figure}

		According to our observation, typical data manipulations on numerical data will lead to the drift of its distribution. For example, a Taobao online seller's transaction records can be ``click farmed'' to increase the volume of sales. Fig.~\ref{fig:example-ecdf} shows the sales distribution within one day. The curve for cheated data is emulated according to a popular method for click farming. It can be observed that there exists clearly a gap between these two distributions. 		
		%For example, in a sampled data set from Melbourne city pedestrian volume along main streets\footnote{https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp}, 20\% records were randomly selected and modified, the value set as a tenth of the original. The empirical cumulative distribution function of the two data sets are shown in Fig.~\ref{fig:example}, where there is clearly a gap between these distributions.
		These anomalies inside data pipelines will severely affect mining and learning algorithms and further change the final decision given by the entire system.
